\section{Effort Spent}

We worked a lot together in order to take care of every relevant aspect that a multi-tier architecture requires. In details, each group memeber focused on the following aspects, working around 80-90 hours:

\begin{itemize}
	\item \textbf{Gugliemo Menchetti}: worked mainly on the external API integration on the server side. In details, he implemented the interfaces for the following services:
	\begin{itemize}
		\item Google Maps
		\item Mapbox
		\item Uber
		\item Gmail
	\end{itemize}
	He implemented the logic concerning the booking functionalities of the application. He performed the unit and integration tests for the interfaces and the booking API.
	
	\item \textbf{Lorenzo Norcini}: developed the back end part of the system. He defined the database schemas and he implemented the application logic for what concerns the menagment of the schedule, the feasibility manager and the design of the API endpoints. He also performed unit and integration tests for the components he developed. 
	
	\item \textbf{Tommaso Scarlatti}: developed the iOS application, designing the user interface, the logo and the UX workflow. He managed the HTTP requests on the client side, taking into account possible exceptions due to the asynchronous response. He implemented the location search through the Apple MapKit framework and the in-app Uber login. He also wrote the system tests, testing the integration of the client application and the APIs provided by the server.

\end{itemize}

Furthermore, we worked together on the following aspects:

\begin{itemize}
	\item Decide among the requirements defined in the RASD which one to implement in the prototype
	\item External services to be used
	\item Database structure details
	\item System integration
	\item ITD design
\end{itemize}